maze-dataset

### 2025-04-08 docs/paper/paper.tex
messing with page layout

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ maze\_dataset }\ImportTok{import}\NormalTok{ (}
\NormalTok{  MazeDataset, MazeDatasetConfig, LatticeMazeGenerators}
\NormalTok{)}
\CommentTok{\# create a config}
\NormalTok{cfg: MazeDatasetConfig }\OperatorTok{=}\NormalTok{ MazeDatasetConfig(}
\NormalTok{    name}\OperatorTok{=}\StringTok{"example"}\NormalTok{, }\CommentTok{\# names need not be unique, filenames are automatically made to be}
\NormalTok{    grid\_n}\OperatorTok{=}\DecValTok{3}\NormalTok{,   }\CommentTok{\# size of the maze}
\NormalTok{    n\_mazes}\OperatorTok{=}\DecValTok{32}\NormalTok{, }\CommentTok{\# number of mazes in the dataset}
\NormalTok{    maze\_ctor}\OperatorTok{=}\NormalTok{LatticeMazeGenerators.gen\_dfs, }\CommentTok{\# many algorithms available}
    \CommentTok{\# (optional) algorithm{-}specific parameters}
\NormalTok{    maze\_ctor\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"do\_forks"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\}, }
    \CommentTok{\# (optional) many options for restricting start/end points}
\NormalTok{    endpoint\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"deadend\_start"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\},}
\NormalTok{)}
\CommentTok{\# create a dataset}
\NormalTok{dataset: MazeDataset }\OperatorTok{=}\NormalTok{ MazeDataset.from\_config(}
\NormalTok{  cfg, }\CommentTok{\# pass the config}
\NormalTok{  ..., }\CommentTok{\# other options such as whether to load from disk,}
       \CommentTok{\# generate in parallel, etc.}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

When initializing mazes, further configuration options can be specified
through the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.from_config}{\texttt{from\_config()}}
factory method as necessary. Options allow for saving/loading existing
datasets instead of regenerating, and parallelization options for
generation. Available maze generation algorithms are static methods of
the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators}{\texttt{LatticeMazeGenerators}}
class and include generation algorithms based on randomized depth-first
search, Wilson's algorithm (\protect\hyperlink{ref-wilson}{Wilson,
1996}), percolation (\protect\hyperlink{ref-percolation}{Duminil-Copin,
2017}; \protect\hyperlink{ref-percolation-clustersize}{Fisher \& Essam,
2004}), Kruskal's algorithm
(\protect\hyperlink{ref-kruskal1956shortest}{Kruskal, 1956}), and
others.

@@

@@

\begin{figure}[H]
  \centering
  \begin{tabular}{p{1.5in} p{1.5in} p{1.5in}} 
    \hline \\[.5em]
    % algorithms
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_ascii}{\texttt{as\_ascii()}}
    & \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_pixels}{\texttt{as\_pixels()}}
    & \href{https://understanding-search.github.io/maze-dataset/maze_dataset/plotting.html\#MazePlot}{\texttt{MazePlot()}} \\[.5em]
    % descriptions
      Simple text format for displaying mazes, useful for debugging in a terminal environment.
      & \texttt{numpy} array of \texttt{dtype=uint8} and shape \texttt{(height, width, 3)}. The last dimension is RGB color.
      & feature-rich plotting utility with support for multiple paths, heatmaps over positions, and more. \\[1em]
    \hline \\
    % examples
      \multicolumn{1}{c}{\begin{minipage}[b]{1.6in}
        \setlength{\baselineskip}{0.9em}
        \input{figures/outputs-ascii-colored.tex} 
      \end{minipage}}
      & \multicolumn{1}{c}{
        \includegraphics[width=0.25\textwidth]{figures/outputs-pixels.pdf}
      }
      & \multicolumn{1}{c}{
        \includegraphics[width=0.25\textwidth, trim={0 0 -.3cm, -.5cm}, clip]{figures/outputs-mazeplot.pdf}
      } \\[1em]

    \hline \\
  \end{tabular}
  \caption{Various output formats. Top row (left to right): ASCII diagram, rasterized pixel grid, and advanced display.}
  \label{fig:output-fmts}
\end{figure}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ maze\_dataset }\ImportTok{import}\NormalTok{ (}
\NormalTok{  MazeDataset, MazeDatasetConfig, LatticeMazeGenerators}
\NormalTok{)}
\CommentTok{\# create a config}
\NormalTok{cfg: MazeDatasetConfig }\OperatorTok{=}\NormalTok{ MazeDatasetConfig(}
\NormalTok{    name}\OperatorTok{=}\StringTok{"example"}\NormalTok{, }\CommentTok{\# names need not be unique}
\NormalTok{    grid\_n}\OperatorTok{=}\DecValTok{3}\NormalTok{,   }\CommentTok{\# size of the maze}
\NormalTok{    n\_mazes}\OperatorTok{=}\DecValTok{32}\NormalTok{, }\CommentTok{\# number of mazes in the dataset}
\NormalTok{    maze\_ctor}\OperatorTok{=}\NormalTok{LatticeMazeGenerators.gen\_dfs, }\CommentTok{\# many algorithms available}
    \CommentTok{\# (optional) algorithm{-}specific parameters}
\NormalTok{    maze\_ctor\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"do\_forks"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\}, }
    \CommentTok{\# (optional) many options for restricting start/end points}
\NormalTok{    endpoint\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"deadend\_start"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\},}
\NormalTok{)}
\CommentTok{\# create a dataset}
\NormalTok{dataset: MazeDataset }\OperatorTok{=}\NormalTok{ MazeDataset.from\_config(}
\NormalTok{  cfg, }\CommentTok{\# pass the config}
\NormalTok{  ..., }\CommentTok{\# other options such as whether to load from disk,}
       \CommentTok{\# generate in parallel, etc.}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

When initializing a dataset, options which do not affect the mazes
themselves can be specified through the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.from_config}{\texttt{from\_config()}}
factory method as necessary. These options allow for saving/loading
existing datasets instead of re-generating, parallelization options for
generation, and more. Available maze generation algorithms are static
methods of the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators}{\texttt{LatticeMazeGenerators}}
namespace class and include generation algorithms based on randomized
depth-first search, Wilson's algorithm
(\protect\hyperlink{ref-wilson}{Wilson, 1996}), percolation
(\protect\hyperlink{ref-percolation}{Duminil-Copin, 2017};
\protect\hyperlink{ref-percolation-clustersize}{Fisher \& Essam, 2004}),
Kruskal's algorithm
(\protect\hyperlink{ref-kruskal1956shortest}{Kruskal, 1956}), and
others.

@@

For use cases where mazes of different sizes, generation algorithms, or
other parameter variations are required, we provide the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/collected_dataset.html\#MazeDatasetCollection}{\texttt{MazeDatasetCollection}}
class, which allows for creating a single iterable dataset from multiple
independent configurations.

@@

\begin{figure}[H]
  \centering
  \begin{tabular}{p{1.5in} p{1.5in} p{1.5in}} 
    \hline \\[.5em]
    % algorithms
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_ascii}{\texttt{as\_ascii()}}
    & \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_pixels}{\texttt{as\_pixels()}}
    & \href{https://understanding-search.github.io/maze-dataset/maze_dataset/plotting.html\#MazePlot}{\texttt{MazePlot()}} \\[.5em]
    % descriptions
      Simple text format for displaying mazes, useful for debugging in a terminal environment.
      & \texttt{numpy} array of \texttt{dtype=uint8} and shape \texttt{(height, width, 3)}. The last dimension is RGB color.
      & feature-rich plotting utility with support for multiple paths, heatmaps over positions, and more. \\[1em]
    \hline \\
    % examples
      \multicolumn{1}{c}{\begin{minipage}[b]{1.6in}
        \setlength{\baselineskip}{0.9em}
        \input{figures/outputs-ascii-colored.tex} 
      \end{minipage}}
      & \multicolumn{1}{c}{
        \includegraphics[width=0.25\textwidth]{figures/outputs-pixels.pdf}
      }
      & \multicolumn{1}{c}{
        \includegraphics[width=0.27\textwidth, trim={0 0.8cm -.3cm, -.5cm}, clip]{figures/outputs-mazeplot.pdf}
      } \\[1em]

    \hline \\
  \end{tabular}
  \caption{Various output formats. Top row (left to right): ASCII diagram, rasterized pixel grid, and advanced display tool.}
  \label{fig:output-fmts}
\end{figure}
